---
title: "551_eda"
author: "Brendan Matthys"
date: "12/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
```

```{r}
tidyselect::starts_with(data$budget,vars = '$')
```


```{r}
#subset(data, grepl('^$',data$budget))


data

```


```{r}
data <- read.csv('/Users/brendanmatthys/Desktop/imdb-movies-bayesian-analysis/data-collection/cleaned_data.csv')

data$budget[data$budget == ""] <- NA
data <- data|>
  filter(!is.na(budget))


data <- data|>
  filter(stringr::str_starts(budget, fixed('$')))
#data <- subset(data, str_contains(data$budget,'$'))

data$budget <- parse_number(data$budget, na = c("", "NA"))
data$revenue <- parse_number(data$revenue, na = c("", "NA"))


data = subset(data, select = c(-X))
data <- data|>
  filter(!is.na(revenue))



data <- subset(data, genres %in% c('Drama','Comedy','Horror','Documentary','Thriller',
'Action','Romance', 'Western'))

data$release_date <- as.Date(data$release_date)
```

```{r}
data
```

```{r}


#data$budget <- data$budget %>% mutate_all(na_if,"")

#
data
```


```{r}






#data <- subset(data, main_country = "United States")



```

```{r}
data
```



```{r}

data$release_month <- as.factor(data$release_month)
```


Budget looks ugly rn. let's change that. also date isn't a date yet 
```{r}
# data$revenue <- as.integer(data$revenue)
# data$budget <- as.integer(data$budget)




```



```{r}
set.seed(52996)
training_data <- data |>
  group_by(genres)|>
slice_sample(prop = 0.7) 

training_data
```


```{r}
testing_data <- anti_join(data, training_data, by = "imdb_id")
testing_data
```


```{r}
data
```

```{r}
#is there a correlation between budget and revenue?
cor(data$budget, data$revenue, use = "complete.obs")
```
That is interesting, I was expecting some sort of correlation.

```{r}
summary(lm(revenue~budget, data = data))
```
But budget does have a significant linear relationship to revenue. However, that coefficient is nearly 0.




```{r}
revenue_month <- training_data |>
  group_by(release_month)|>
  summarise(median(revenue))
  #arrange(as.integer(release_month))
colnames(revenue_month) <- c('release_month', 'median_revenue')
head(revenue_month,12)
```

```{r}
data |>
  group_by(release_month)|>
  summarise(n(),mean(revenue, na.rm = TRUE),median(revenue, na.rm = TRUE))
```





Now let's examine to see if the "summer blockbuster" trend is legit.

```{r}
training_data
```


```{r}
ggplot(data = training_data, aes(x = reorder(release_month,as.integer(release_month)), y = median(revenue))) + geom_bar(stat = "identity") + labs(title = "Median Opening Weekend Revenue per Month",x = "Month", y = "Median Opening Weekend Revenue") + facet_wrap(~genres)
```



Yeah, looks to be legit. The revenue for summer is much higher than the other months.

I'm curious if this trend exists per year as well. I think inflation would increase the opening weekend revenue, but let's find out 

```{r}
revenue_year <- training_data |>
  group_by(release_year)|>
  summarise(median(revenue))|>
  arrange(as.integer(release_year))
colnames(revenue_year) <- c('release_year', 'median_revenue')
revenue_year
```





```{r}
ggplot(training_data) + geom_boxplot(aes(x = release_month, y = revenue)) +  ylim(c(0,2500000)) +  facet_wrap(~genres)
#boxplot(as.integer(training_data$release_month))
```

```{r}
ggplot(training_data) + geom_point(aes(x = duration, y = revenue))  + ylim(c(0,2500000)) +  facet_wrap(~genres, scale = "free")
```




```{r}
ggplot(training_data) + geom_point(aes(x = budget, y = revenue))   +  facet_wrap(~genres)
```
```{r}
ggplot(training_data) + geom_point(aes(x = release_year, y = revenue))   +  facet_wrap(~genres)
```

```{r}
data$release_year <- as.integer(data$release_year)
```


```{r}
subset(training_data) |>
  group_by(genres,release_month) |>
  summarise(n())
  
```

This is hard to examine with the one movie in 1905. For visualization purposes let's exclude that right now.

```{r}
ggplot(data = subset(revenue_year, release_year > 1960), aes(x = reorder(release_year,as.integer(release_year)), y = median_revenue)) + geom_point(stat = "identity") + labs(title = "Median Opening Weekend Revenue per Year",x = "Year", y = "Median Opening Weekend Revenue") 
```


This is very odd, let's see how many movies we have per year per se

```{r}
data |>
  group_by(release_year)|>
  summarise(n)|>
  arrange(as.integer(release_year))
```
We only want single genre movies
```{r}
genrestotal <- data |>
  group_by(genres)|>
  summarise(n())|>
  filter(!str_detect(genres, ';'))

colnames(genrestotal) <- c('genre','total')
genrestotal|>
  arrange(-total)

```

We shall use Drama, Comedy, and Horror. Documentary won't really have too much of a box office presence here.

```{r}
ggplot()
```


```{r}
# ggplot(subset(training_data, genres %in% c('Drama','Comedy','Horror')), aes(x=release_date, y=revenue, color = genres)) +
#   geom_point() + 
#   xlab("Date") + ylab("Revenue") + labs(title = "Largest Opening Revenues") +geom_text(training_data,revenue>51000000),
#             aes(label=title,size = 3, vjust = 2, hjust = 1)

```


```{r}
subset(training_data, release_month == 8) |>
  arrange(-revenue)
```














```{r}
ggplot(training_data, aes(x = duration, y = revenue)) + geom_point(stat = "identity") + labs(title = "Median Opening Weekend Revenue per Year",x = "Duration", y = "Median Opening Weekend Revenue") 
```



